\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color,xcolor}
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{00008B}
\definecolor{shade}{HTML}{D4D7FE}      %light blue shade
\definecolor{text1}{HTML}{000000}      %text is black
\definecolor{headings}{HTML}{00008B}   %navy blue
\hypersetup{   colorlinks,breaklinks,
               urlcolor=linkcolor,
               linkcolor=linkcolor
}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Joseph Randall Hunt}  & 650.690.0657\\
144 Avonlea Pl &  randallhunt@gmail.com\\
Johnson City, TN  37604& http://www.ranman.org/\\
\end{tabular*}
\\

\vspace{0.1in}
\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Western Carolina University}{Cullowhee, NC}{B.S., Computer Science}{Aug. 2009 -- May. 2012}
	\begin{itemize}
		\resitem{Relevant courses: Data Structures, Software Engineering, Wireless Sensor Networks, Internet Security and Ethics, Computer Graphics, Calculus, Discrete Mathematics, Statistics, Computer Networking, Computer Organization}
	\end{itemize}
\item
	\ressubheading{Punahou Academy}{Honolulu, HI}{High School}{2005--2009}
	\begin{itemize}
		\resitem{Graduated with Honors. Dean's list every year. One of four seniors out of 400 selected for special recognition by the faculty. High scores on SAT/ACT/AP exams.}
	\end{itemize}
\end{itemize}
\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{\href{http://fondu.com/}{SpotOn/Fondu}}{New York, NY}{Software Engineer}{May 2011 -- Oct. 2011}
	\begin{itemize}
		\resitem{As part of a HackNY Fellowship, designed and implemented a collaborative filtering recommendation engine in Python and C which improved recommendation speed (response and pre-calculations) by 800\%. Used SciPy,NumPy,and Weave to dramatically increase speed.}
		\resitem{Wrote scripts to automate deployment and logging of Amazon Web Services. Used the boto (and fabric) Python framework.}
		\resitem{Designed and coded the company landing page.}
	\end{itemize}
\item
   \ressubheading{NASA Ames Research Center}{Mountain View, CA}{Software Engineer}{Jan. 2011--May. 2011}
   \begin{itemize}
      \resitem{Created an KML Tour generator and editor using Django, Python, SQL, and Javascript.}
      \resitem{Programmed a specialized media import tool which pulls media and meta-data from several different sources into a central database. Project generated a whole new set of data products for the maps team.}
      \resitem{Worked on team of two to develop better navigation algorithms for rovers.}
   \end{itemize}
\item
   \ressubheading{NASA Langley Research Center}{Hampton, VA}{Software Engineer}{May 2010--Aug. 2010}
      \begin{itemize}
         \resitem{Worked on several tools for mass properties evaluation
         which culminated in the design of a mass properties API.} 
         \resitem{Also worked
         with an 8 person team to design and perform a series of tests on
         a flotation concept. Project could save ~2.5 million dollars if implemented.
         Findings were published to NASA's main web-page, AIAA
         newsletter, and several other notable websites.}
      \end{itemize}
\item
   \ressubheading{Western Carolina University}{Cullowhee, NC}{Various Roles}{Aug. 2009--May 2011}
      \begin{itemize}
         \resitem{Resolved IT issues for students and faculty. Also taught several workshops on web development.}
         \resitem{Assisted professor and students in introductory computer science courses as a TA.}
         \resitem{Deployed Drupal based sites for clubs, teams, and organizations.}
         \resitem{Maintained the computer science lab computers running Linux, Windows, and OSX with several VMs. Created scripts to automatically update and backup all computers and all VMs. Managed backups leading to a 5\% decrease in downtime from previous administrator.}
      \end{itemize}
\end{itemize}

\pagebreak
\resheading{Skills}
\begin{description}
\item[Languages:]
C, Java, Python, Javascript, PHP, Ruby, Go, Prolog, HTML/CSS, SQL, LISP, MIPS, Objective-C, French, German, Spanish
\item[Systems/Tools:]
OS X, Linux (CentOS, Gentoo, Ubuntu), Windows, MySQL, MongoDB, vim, emacs, XCode
\item[Frameworks/Platforms/APIs:]
jQuery, nodejs, django, rails, SciPy, NumPy, Foursquare API, Facebook APIs, Google APIs, drupal, wordpress, heroku, twilio 
\end{description}

\resheading{Honors/Awards/Presentations}
\begin{itemize}
   \resitem{\href{http://www.youtube.com/watch?v=ga6RPRAFRUY}{Third Place HackNY Fall 2011 Hackathon}(out of 25 teams and 200 competitors)}
   \resitem{\href{http://hackny.org/a/about/}{HackNY Fellow} (one of 35 students selected to intern at NYC startups)}
   \resitem{Deans List, Honors College}
   \resitem{Featured in Honors College ``Imagine'' magazine}
   \resitem{Student Representative on Academic Technology Committee}
   \resitem{AP Scholar's Award}
   \resitem{Several presentations at NASA}
\end{itemize}
\resheading{Activities and Societies}
\begin{itemize}
   \resitem{IEEE Member}
   \resitem{\href{http://polaris.cs.wcu.edu/~acm/}{Student ACM Chapter}}
   \resitem{\href{https://github.com/ranman}{Open-Source Contributor}}
   \resitem{Active on \href{http://stackoverflow.com/users/240004/ranman}{StackOverflow}}
   \resitem{Passionate about Robotics
      \href{http://robotics.punahou.edu/}{[1]}
      \href{http://irg.arc.nasa.gov}{[2]}}
   \resitem{\href{http://www.youtube.com/user/ranman96734}{Rubik's Cubes}}
\end{itemize}
\resheading{Relevant Coursework and Independent Projects}
\begin{itemize}
   \resitem{\href{http://www.mosaicmachine.com/}{Mosaic Machine} in Javascript}
   \resitem{\href{http://www.locreep.com/}{LoCreep} in Python, Javascript, and NodeJS}
   \resitem{Multiuser Chat System in Java}
   \resitem{Set Associative Cache Simulator in Java}
   \resitem{Tokenizer and Parser in C}
   \resitem{Wireless Sensor Grapher in TinyC+Java}
   \resitem{TCP Implementation in TinyC}
   \resitem{Adventure Game in Prolog}
\end{itemize}
\end{document}